Supporting Information: Chemically Selective Transport in a Cross-Linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-06-25 Ben_Manuscripts/transport/Supporting_Information.tex
Minor figure changes
New figures and modifications for response to reviewers
Formatted, addded affiliations and fixed title

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}

\externaldocument[M-]{Outline}

@@

\title{Supporting Information: Chemically Selective Transport in a Cross-linked 
H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

  Since the equilibrium water content is unclear based on the previous
  simulations, we elected to choose and study systems with two different water
  contents. We removed the water reservoir and allowed the pore and tail water
  contents to equilibrate with 5 and 10 wt \% total water. We placed one third of
  the total water needed in the tails, based on the intuition gained in
  Figure~\ref{fig:gap_prefilled_equil}. We considered the water content
  equilibrated once the water contents plateaued. The 5 wt\% system did
  not plateau until $\sim$ 600 ns (Figure~\ref{fig:5wt_offset_equil})
  while the 10 wt \% water system equilibrated within the first 100 ns of 
  simulation (Figure~\ref{fig:10wt_offset_equil}).
  The pores contain 72 \% and 69 \% of the total water in the 5 and 10 wt \%
  systems respectively.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
% Generated with solute_partitioning.py -t full_shifted.xtc -g berendsen.gro -r SOL -pr 1.6 --savename water_partitioning.pl
% in directory /home/bcoscia/Documents/Gromacs/equilibration/solvation_equilibration/NaGA3C11/offset/5wt
  \includegraphics[width=\textwidth]{5wt_offset_equil.pdf}
  \caption{5 wt \%}\label{fig:5wt_offset_equil}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{10wt_offset_equil.pdf}
  \caption{10 wt \%}\label{fig:10wt_offset_equil}
% Generated with solute_partitioning.py -t shifted.xtc -g last.gro -r SOL -pr 1.48 --savename water_partitioning.pl
% in directory /home/bcoscia/Documents/Gromacs/equilibration/solvation_equilibration/NaGA3C11/offset/10wt
  \end{subfigure}
  \caption{We created solvated systems with one third of the total water
	  initially placed in the tail region. (a) With 5 wt \% total water, the water
	  content equilibrates after 600 ns, with $\sim$ 72 \% of the total water in the
	  pores. (b) With 10 wt \% total water, the water content equilibrates after 100
	  ns, with $\sim$ 69 \% of the total water in the
	  pores.}\label{fig:solvation_equilibration}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
% Generated with solute_partitioning.py -t PR.trr -g PR.gro -r SOL --savename SOL_partitioning.pl
% In directory /home/bcoscia/Documents/Gromacs/equilibration/xlink_equilibration/NaGA3C11/5wt
  \includegraphics[width=\textwidth]{5wt_offset_xlinked_equil.pdf}
  \caption{5 wt\%}\label{fig:5wt_offset_xlinked_equil}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{10wt_offset_xlinked_equil.pdf}
  \caption{10 wt\%}\label{fig:10wt_offset_xlinked_equil}
% Generated with solute_partitioning.py -t xlinked_equil.trr -g xlinked_equil.gro -r SOL -pr 1.48 --savename water_partitioning.pl
% In directory /home/bcoscia/Documents/Gromacs/equilibration/xlink_equilibration/NaGA3C11/10wt/63_percent
  \end{subfigure}
  \caption{The water content in the tail and pore region is not affected
  by cross-linking}\label{fig:solvation_equilibration}
  \end{figure}

  \section{Solute Interaction}\label{section:solute_interaction}

@@

%  \subsection{Sensitivity of Breakdown radius of Stokes-Einstein Equation}\label{section:se_sensitivity}
%  
%  In the main text, we estimated the trend in solute MSDs using the Stokes-Einstein
%  equation with the correction factor of Gierer and Wirtz, $f$, given by 
%  equation~\ref{M-eqn:correction_factor}. As $r \rightarrow \infty$ , $f \rightarrow 1$.
%  
%  We assumed that the Stokes-Einstein relationship could be approximated as a
%  piecewise function where the correction factor of Gierer and Wirtz, $f$, given
%  by equation~\ref{M-eqn:correction_factor} of the main text, is only applied below
%  a critical radius. At radii greater than the critical radius, $f$ = 1.
%  
%  In the main text, we constrained the corrected Stokes-Einstein equation so that
%  it passed through the highest MSD value. We also plotted the uncorrected 
%  Stokes-Einstein equation ($f$=1) as a lower bound to our expectations for 
%  unrestricted solute motion. The lower bound is relatively insensitive to our
%  choice of critical radius. Even for an unrealistically small critical radius 
%  of 0.5 nm, the curve is within
%  
%  \begin{figure}[!htb]
%  \centering
%  \includegraphics[width=0.45\textwidth]{stokes_intersection_sensitivity.pdf}
%  \caption{We varied the molecular radius at which we assumed the Stokes-Einstein
%  (SE) relationship to breaks down. It is assumed that the Gierer and Wirtz correction
%  to the SE equation becomes a more accurate estimation of MSD at small radii, after
%  the point of intersection }\label{fig:se_intersection_sensitivity}
%  \end{figure}
  \clearpage
  \section{Solute MSD Ranking Time Lag Sensitivity}\label{section:lag_sensitivity}

  We chose to report the MSD of our solutes after a 400 ns time lag. This choice does
  not have a significant influence on the ranking of the solute MSDs. Although there
  is minor re-ranking among solutes with similar MSDs, it does not affect any of 
  the conclusions drawn in the main text.

@@

  \clearpage
  \section{Pore Region Definition}\label{section:pore-region}

@@

  \begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{pore_cutoff.pdf}
  \caption{Defining the cut-off 0.75 nm from the pore center maximizes the 
  difference in hop lengths between solutes in and out of the pore. We 
  varied the location of the cut-off defining the edge of the pore region
  in increments of 0.05 from 0.3 to 0.7. We varied the cut-off in 
  increments of 0.01 from 0.7 to 0.8 in order to increase our resolution
  about the maximum.}\label{fig:pore_cutoff}
  \end{figure}

>>>>

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}
\usepackage{authblk}

\externaldocument[M-]{Final_Draft}

@@

\title{Supporting Information: Chemically Selective Transport in a Cross-Linked 
H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\author[1]{Benjamin J. Coscia}
\author[1]{Michael R. Shirts} 
\date{E-mail: michael.shirts@colorado.edu}

\affil[1]{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}

@@

  Since the equilibrium water content is unclear based on the previous
  simulations, we elected to choose and study systems with two different water
  contents. We removed the water reservoir and allowed the pore and tail water
  contents to equilibrate with 5 and 10 wt \% total water. We placed one third of
  the total water needed in the tails, based on the intuition gained in
  Figure~\ref{fig:gap_prefilled_equil}. We considered the water content
  equilibrated once the water contents plateaued. The 5 wt\% system did
  not plateau until $\sim$ 600 ns (Figure~\ref{fig:5wt_offset_equil})
  while the 10 wt \% water system equilibrated within the first 100 ns of 
  simulation (Figure~\ref{fig:10wt_offset_equil}).
  The pores contain 72 \% and 69 \% of the total water in the 5 and 10 wt \%
  systems respectively.
  \clearpage
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
% Generated with solute_partitioning.py -t full_shifted.xtc -g berendsen.gro -r SOL -pr 1.6 --savename water_partitioning.pl
% in directory /home/bcoscia/Documents/Gromacs/equilibration/solvation_equilibration/NaGA3C11/offset/5wt
  \includegraphics[width=\textwidth]{5wt_offset_equil.pdf}
  \caption{5 wt \%}\label{fig:5wt_offset_equil}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{10wt_offset_equil.pdf}
  \caption{10 wt \%}\label{fig:10wt_offset_equil}
% Generated with solute_partitioning.py -t shifted.xtc -g last.gro -r SOL -pr 1.48 --savename water_partitioning.pl
% in directory /home/bcoscia/Documents/Gromacs/equilibration/solvation_equilibration/NaGA3C11/offset/10wt
  \end{subfigure}
  \caption{We created solvated systems with one third of the total water
	  initially placed in the tail region. (a) With 5 wt \% total water, the water
	  content equilibrates after 600 ns, with $\sim$ 72 \% of the total water in the
	  pores. (b) With 10 wt \% total water, the water content equilibrates after 100
	  ns, with $\sim$ 69 \% of the total water in the
	  pores.}\label{fig:solvation_equilibration}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
% Generated with solute_partitioning.py -t PR.trr -g PR.gro -r SOL --savename SOL_partitioning.pl
% In directory /home/bcoscia/Documents/Gromacs/equilibration/xlink_equilibration/NaGA3C11/5wt
  \includegraphics[width=\textwidth]{5wt_offset_xlinked_equil.pdf}
  \caption{5 wt\%}\label{fig:5wt_offset_xlinked_equil}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{10wt_offset_xlinked_equil.pdf}
  \caption{10 wt\%}\label{fig:10wt_offset_xlinked_equil}
% Generated with solute_partitioning.py -t xlinked_equil.trr -g xlinked_equil.gro -r SOL -pr 1.48 --savename water_partitioning.pl
% In directory /home/bcoscia/Documents/Gromacs/equilibration/xlink_equilibration/NaGA3C11/10wt/63_percent
  \end{subfigure}
  \caption{The water content in the tail and pore region is not affected
  by cross-linking}\label{fig:xlinked_solvation_equilibration}
  \end{figure}

  \clearpage
  \section{Solute Interaction}\label{section:solute_interaction}

@@

%  \subsection{Sensitivity of Breakdown radius of Stokes-Einstein Equation}\label{section:se_sensitivity}
%  
%  In the main text, we estimated the trend in solute MSDs using the Stokes-Einstein
%  equation with the correction factor of Gierer and Wirtz, $f$, given by 
%  equation~\ref{M-eqn:correction_factor}. As $r \rightarrow \infty$ , $f \rightarrow 1$.
%  
%  We assumed that the Stokes-Einstein relationship could be approximated as a
%  piecewise function where the correction factor of Gierer and Wirtz, $f$, given
%  by equation~\ref{M-eqn:correction_factor} of the main text, is only applied below
%  a critical radius. At radii greater than the critical radius, $f$ = 1.
%  
%  In the main text, we constrained the corrected Stokes-Einstein equation so that
%  it passed through the highest MSD value. We also plotted the uncorrected 
%  Stokes-Einstein equation ($f$=1) as a lower bound to our expectations for 
%  unrestricted solute motion. The lower bound is relatively insensitive to our
%  choice of critical radius. Even for an unrealistically small critical radius 
%  of 0.5 nm, the curve is within
%  
%  \begin{figure}[!htb]
%  \centering
%  \includegraphics[width=0.45\textwidth]{stokes_intersection_sensitivity.pdf}
%  \caption{We varied the molecular radius at which we assumed the Stokes-Einstein
%  (SE) relationship to breaks down. It is assumed that the Gierer and Wirtz correction
%  to the SE equation becomes a more accurate estimation of MSD at small radii, after
%  the point of intersection }\label{fig:se_intersection_sensitivity}
%  \end{figure}

  \section{Solute MSD Ranking Time Lag Sensitivity}\label{section:lag_sensitivity}

  We chose to report the MSD of our solutes after a 400 ns time lag. This choice does
  not have a significant influence on the ranking of the solute MSDs (see 
  Figure~\ref{fig:lag_sensitivity}). Although there is minor re-ranking among solutes
  with similar MSDs, it does not affect any of the conclusions drawn in the main text.

@@

  \section{Pore Region Definition}\label{section:pore-region}

@@

  \begin{figure}[H]
  \centering
  \includegraphics[width=0.5\linewidth]{pore_cutoff.pdf}
  \caption{Defining the cut-off 0.75 nm from the pore center maximizes the 
  difference in hop lengths between solutes in and out of the pore. We 
  varied the location of the cut-off defining the edge of the pore region
  in increments of 0.05 from 0.3 to 0.7. We varied the cut-off in 
  increments of 0.01 from 0.7 to 0.8 in order to increase our resolution
  about the maximum.}\label{fig:pore_cutoff}
  \end{figure}
